Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
removing linear operator equations slides
updating krylov slide

%%---------------------------------------------------------------------------%%
\begin{frame}{Linear Operator Equations}

  \begin{itemize}
  \item We seek solutions of the general linear operator equation
  \end{itemize}

  \[
  \ve{A} \ve{x} = \ve{b}
  \]
  \[
  \ve{A} \in \mathbb{R}^{N \times N},\ \ve{A} : \mathbb{R}^{N}
  \rightarrow \mathbb{R}^{N},\ \ve{x} \in \mathbb{R}^N,\ \ve{b} \in
  \mathbb{R}^N
  \]

  \[
  \ve{r} = \ve{b} - \ve{A}\ve{x}
  \]

  \begin{itemize}
  \item $\ve{r}=\ve{0}$ when an exact solution is found
  \end{itemize}

  \medskip \medskip 
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {A Requirement} Assert that $\ve{A}$ is \textit{nonsingular}. The
    solution is then:
    \[
    \ve{x} = \ve{A}^{-1}\ve{b}
    \]
  \end{beamerboxesrounded}

@@

  \medskip \medskip \medskip
  \small{
  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
    \medskip
  \item Must generate an orthonormal basis for
    $\mathcal{K}_m(\ve{A},\ve{r}_0)$
    \medskip
  \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
    or Lanzcos
    \medskip
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}
  }

>>>>

@@

  \medskip \medskip \medskip
  \small{
  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
    \medskip
  \item Require only the action of the operator
    \medskip
  \item Must generate an orthonormal basis for
    $\mathcal{K}_m(\ve{A},\ve{r}_0)$
    \medskip
  \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
    or Lanzcos
    \medskip
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}
  }
